Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-23 ms.tex
added some more material about K Masuda's reduction.

\subsection{Comparison to BOSZ}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
These high resolution spectra can be compared to the BOSZ models which are calculated up to $R = 300,000$.
The BOSZ models \citep{bohlin2017bosz} are calculated up to a resolution of 300,000, so we use these to compare to the measured spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.

>>>>

\subsection{Independent Reduction}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
